### 2024-01-24 Paper/main.tex
add new images to paper
add images to paper
add packages and change importname of the last plot

\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\bibliography{shortbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set this to true to remove the border
    linkcolor=black, % Color for internal links
    citecolor=black, % Color for citations
    }
\usepackage{listings}
\usepackage{blindtext}
\usepackage{cleveref}
\usepackage{subcaption}
\geometry{margin=25mm}
\begin{document}

@@

@@

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.7\textwidth}
        \centering
        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_10_model.pgf}}
        \caption{Loss of model with filesize 10}
        \label{fig:loss_comparison_filesize_10}
    \end{minipage}\hfill
    \begin{minipage}{0.7\textwidth}
        \centering
        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_mixed_model.pgf}}
        \caption{Loss of mixed model}
        \label{fig:loss_comparison_filesize_mixed}
    \end{minipage}
\end{figure}

>>>>

\documentclass{article}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{pgfplots}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\bibliography{shortbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set this to true to remove the border
    linkcolor=black, % Color for internal links
    citecolor=black, % Color for citations
    }
\usepackage{listings}
\usepackage{blindtext}
\usepackage{cleveref}
\usepackage{subcaption}
\geometry{margin=25mm}
\begin{document}

@@

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \resizebox{\textwidth}{!}{\input{../Plots/psnr_adapted.pgf}}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \resizebox{\textwidth}{!}{\input{../Plots/ssim_adapted.pgf}}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_filtered.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_withoutMixed.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.7\textwidth}
        \centering
        \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_fs_10_model.pgf}}
         \caption{Loss of model with filesize 10}
         \label{fig:loss_comparison_filesize_10}
     \end{minipage}\hfill
     \begin{minipage}{0.7\textwidth}
         \centering
         \resizebox{\textwidth}{!}{\input{../Plots/loss_comparison/loss_comparison_mixed_model.pgf}}
         \caption{Loss of mixed model}
         \label{fig:loss_comparison_filesize_mixed}
    \end{minipage}
\end{figure}
